\section{Discussion}

\subsection{Principal findings}

The extracted literature supports a multidimensional framework for the digital patient spectrum. The most useful axes are the modeled biological scale, degree of patient specificity, temporal orientation, data-coupling mode, modeling approach, function, validation evidence, and maturity. A definition based only on the phrase \emph{digital twin} is too coarse for healthcare, where a static image-based simulation, an in silico trial cohort, and a continuously updated patient replica may be described with adjacent language. Table~\ref{tab:concepts} summarizes the defining attributes reported in the reviews. Their combinations are mapped in Figure~\ref{fig:spectrum}, where dynamic updating, patient specificity, and bidirectional coupling overlap without forming a fixed bundle.

Three reporting discontinuities emerged from the standards-informed crosswalk. First, the digital twin label was more consistent than the operational attributes used to define a twin. Second, deployed or operational language was more common than prospective clinical evidence, external validation, or explicit uncertainty assessment. Table~\ref{tab:validation} details this imbalance. Figure~\ref{fig:validation} displays it across validation approaches and maturity levels. Third, reviews raised broad concerns about interoperability and standardization more often than they reported named standards or semantic mechanisms. The difference is evident when the pipeline and barrier tables are compared (Tables~\ref{tab:pipeline} and~\ref{tab:barriers}). Figures~\ref{fig:pipeline} and~\ref{fig:barriers} show the same contrast graphically. These three discontinuities separate widespread conceptual adoption from the field's evidentiary and infrastructural maturity.

The central translational gap is not lack of enthusiasm but lack of operational specificity. Reviews repeatedly describe personalized care, prediction, diagnosis, monitoring, and treatment planning, while fidelity metrics, validation datasets, uncertainty analysis, reproducibility, interoperability, governance, and workflow integration are reported unevenly. These gaps make it difficult to distinguish a conceptual prototype, research simulation, decision-support artifact, and operational patient twin.

\subsection{Standards-informed interpretation}

The reviewed documents form a modular standards landscape rather than an end-to-end specification for digital patients. ISO/IEC 30173 establishes generic digital twin terminology, and ISO/IEC 30186 provides a generic maturity model.\cite{isoiec2023digitaltwin,isoiec2025maturity} The National Academies consensus report contributes a cross-domain operational definition and emphasizes fit for purpose and continual verification, validation, and uncertainty quantification.\cite{nasem2024digitaltwins} For medical-device submissions, ASME V\&V 40 and the FDA final guidance provide a risk-informed credibility framework centered on a question of interest, a defined context of use, model influence, decision consequence, and evidence adequate for the resulting model risk.\cite{asme2018vv40,fda2023credibility} IMDRF good machine-learning principles add representative datasets, independent testing, human--AI team performance, lifecycle monitoring, and management of retraining and drift for AI-enabled medical devices.\cite{imdrf2025gmlp} These sources apply to different model classes and regulatory contexts; their use here is an interpretive crosswalk, not a retrospective compliance audit.

The first implication is that construct identity and model credibility are separate questions. Dynamic updating and bidirectional interaction help distinguish a twin from a static model or digital shadow, but they do not establish that its predictions are sufficiently accurate, robust, or clinically useful. Conversely, a well-validated virtual patient may be fit for a simulation or training purpose without satisfying a stricter digital twin definition. A two-stage appraisal is therefore more informative: first describe what the construct is and how it interacts with its patient referent; then assess whether the evidence is adequate for the stated use and decision risk.

The second implication is that validation should be treated as a lifecycle process rather than a one-time model-development event. The relatively limited reporting of sensitivity or uncertainty analysis and prospective evidence in Figure~\ref{fig:validation} is important because a patient-linked model may change as the patient, data-generating devices, input distributions, model parameters, or clinical decision task changes. A claim of deployment should therefore be accompanied by model versioning, change control, monitoring thresholds, drift detection, revalidation triggers, and procedures for handling performance degradation. None of these expectations can be inferred from the maturity label alone.

The third implication concerns interoperability. HL7, FHIR, DICOM, and OMOP can support exchange, representation, or harmonization of clinical data, but naming an exchange standard does not establish semantic consistency between models, traceable provenance, or credibility of the resulting predictions. Conversely, the frequent reporting of interoperability as a barrier without named implementation profiles suggests that standardization is often invoked as a general need rather than described as an implemented architecture. Digital patient reporting should therefore identify not only the standard family but also the implementation profile, terminology or ontology, identifiers, transformations, provenance, and conformance testing used at each interface.

\subsection{Implications}

Future work should prioritize a reporting and appraisal standard for digital patient reviews and primary models. The priorities derived from the review in Table~\ref{tab:recommendations} can be sharpened by the standards crosswalk. At minimum, studies should report: the intended purpose and context of use; the physical or biological referent and hierarchy; data provenance, representativeness, and transformations; update frequency and coupling direction; model architecture and version; verification, validation, and uncertainty methods; independence and relevance of validation data; human oversight and workflow role; interoperability profiles and semantic mechanisms; lifecycle monitoring and change control; governance assumptions; and maturity level. The depth of evidence should be proportional to model influence and the consequence of an incorrect decision rather than identical for every educational, research, or clinical application.

The repository structure demonstrates a practical mechanism for that transparency: protocol and adjudication documents are versioned with the extraction workbook; classification rules are explicit; row-level derived data are inspectable; tables and figures are regenerated by one command; and the manuscript imports generated artifacts directly. This arrangement does not replace substantive team adjudication, but it makes every descriptive count auditable and refreshable as extraction evolves.

\subsection{Limitations}

This synthesis is descriptive and does not estimate pooled effects. The extraction workbook contains free-text, multi-label fields with heterogeneous specificity, and regular-expression classification cannot resolve all semantic ambiguity. Counts are therefore record-level signals rather than independent study effects. Some quality-appraisal and reproducibility fields remain incomplete. Title-level duplicate normalization does not substitute for final bibliographic deduplication. Finally, the PRISMA source counts require arithmetic reconciliation before submission, as documented automatically in the generated quality report.

The standards-informed comparison has additional limitations. It was used to interpret the prespecified extraction domains rather than as a prospectively designed compliance instrument. The source documents are heterogeneous: the National Academies report is cross-domain, ISO/IEC standards are generic, ASME and FDA credibility frameworks focus on mechanistic or physics-based medical-device models, and IMDRF principles focus on AI-enabled devices. Moreover, the extraction form did not explicitly code formal context of use, model influence, decision consequence, lifecycle monitoring, drift management, subgroup performance, or human--model team evaluation. Absence of these items from the synthesis may therefore indicate non-reporting, incomplete extraction coverage, or true absence in the underlying literature.

\subsection{Future work}

The next revision should complete team adjudication, reconcile duplicate records and PRISMA counts, finalize author affiliations and declarations, and validate classification rules against a manually reviewed subset. A future extraction update could add structured fields for intended purpose and context of use, model influence and decision consequence, verification distinct from validation, external validation, uncertainty quantification, lifecycle monitoring and versioning, subgroup performance, human factors, and conformance testing. These additions would permit a more direct appraisal of fit-for-purpose credibility while preserving the present spectrum-based taxonomy. The pipeline can then be rerun without changing the manuscript layout.

\section{Conclusion}

Digital patient research is conceptually active but evidentially and infrastructurally immature. Progress toward clinically deployable patient digital twins requires two linked judgments: whether a construct has the operational characteristics claimed for it, and whether it is credible for its intended use. Clearer taxonomy, risk-proportionate and lifecycle validation, interoperable and semantically traceable data architecture, prospective workflow evidence, and governance addressing privacy, equity, accountability, and reproducibility are therefore complementary rather than interchangeable requirements.
